### 2022-04-05 chapters/drto/article.tex
modifs mise en page impression

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{chapters/drto/figures/fig2.jpg}
    \caption{(a) Monthly connectivity indicator between the Marquesas and the DRTO (blue), the Western Marquesas and the DRTO (orange) and the Marquesas and the Western Marquesas (green) between May 2018 and May 2021. Months during which Tortugas gyres were observed in the ocean model outputs are highlighted in grey. Milestones of the observed propagation of the SCTLD through the Marquesas are indicated by dark red dotted lines. (b) Monthly mean currents between the Marquesas and the DRTO between May 2018 and May 2021. Mean ocean circulation with an eastward component is highlighted by red arrows.}
    \label{fig:fig2_drto}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{chapters/drto/figures/fig3.jpg}
    \caption{Edges with largest connection probability to each sub-reef of the DRTO from the Marquesas and the Western Marquesas in November 2020. Connections mostly originated from the southern reefs between the Marquesas and Western Marquesas, and from the northwestern reefs of the Western Marquesas. Reefs are highlighted in light gray while islands are shown in dark gray.}
    \label{fig:fig3_drto}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=.6\textwidth]{chapters/drto/figures/vulnerability_new.png}
    \includegraphics[width=.9\textwidth]{chapters/drto/figures/source_new.png}
    \caption{ (a) Vulnerability indicator value of all sub-reefs of the DRTO in November 2020. Eastern reefs of the DRTO appear most vulnerable to the disease. Locations where the SCTLD was observed in the DRTO are indicated by red stars (b) Source indicator value in November 2020 for every sub-reef of the Marquesas and the Western Marquesas. Northwestern reefs of the Western Marquesas and southern reefs between the Marquesas and the Western Marquesas show a higher transmission potential to the DRTO. Main islands are shown in dark grey, separation between the Marquesas and the Western Marquesas is indicated by a dashed line.}
    \label{fig:fig4_drto}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=.99\textwidth]{chapters/drto/figures/fig2.jpg}
    \caption{(a) Monthly connectivity indicator between the Marquesas and the DRTO (blue), the Western Marquesas and the DRTO (orange) and the Marquesas and the Western Marquesas (green) between May 2018 and May 2021. Months during which Tortugas gyres were observed in the ocean model outputs are highlighted in grey. Milestones of the observed propagation of the SCTLD through the Marquesas are indicated by dark red dotted lines. (b) Monthly mean currents between the Marquesas and the DRTO between May 2018 and May 2021. Mean ocean circulation with an eastward component is highlighted by red arrows.}
    \label{fig:fig2_drto}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.99\textwidth]{chapters/drto/figures/fig3.jpg}
    \caption{Edges with largest connection probability to each sub-reef of the DRTO from the Marquesas and the Western Marquesas in November 2020. Connections mostly originated from the southern reefs between the Marquesas and Western Marquesas, and from the northwestern reefs of the Western Marquesas. Reefs are highlighted in light gray while islands are shown in dark gray.}
    \label{fig:fig3_drto}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=.75\textwidth]{chapters/drto/figures/vulnerability_new.png}
    \includegraphics[width=.99\textwidth]{chapters/drto/figures/source_new.png}
    \caption{ (a) Vulnerability indicator value of all sub-reefs of the DRTO in November 2020. Eastern reefs of the DRTO appear most vulnerable to the disease. Locations where the SCTLD was observed in the DRTO are indicated by red stars (b) Source indicator value in November 2020 for every sub-reef of the Marquesas and the Western Marquesas. Northwestern reefs of the Western Marquesas and southern reefs between the Marquesas and the Western Marquesas show a higher transmission potential to the DRTO. Main islands are shown in dark grey, separation between the Marquesas and the Western Marquesas is indicated by a dashed line.}
    \label{fig:fig4_drto}
\end{figure}

### 2022-04-05 chapters/intro/intro.tex
modifs mise en page impression

\modif{The motion of geophysical fluids such as seawater is characterized by the effects of ambient rotation and stratification \citep{cushman2011introduction}. The ambient rotation is induced by the Earth's spin and generates the Coriolis forces. Stratification arises from the presence of waters with different temperature and salinity, and therefore different density. Under the action of gravitational forces, heavier waters lower while lighter waters rise, which caused the water column to tend towards a stable stratified equilibrium \citep{cushman2011introduction}. However, this equilibrium is disrupted in the presence of discontinuities in horizontal velocities induced by wind and water motion \citep{miles1959generation}. These baroclinic instabilities generate internal waves, water mixing, and eddies \citep{cushman2011introduction}. Eddy activity is especially strong in boundary currents such as the Gulf Stream, where strong horizontal shear occur and where shelf water and deep water masses meet on the shelf break \citep{kourafalou2012florida}. These baroclinic instabilities were shown to have a significant impact on water composition and larval recruitment in the Florida Keys \citep{lee1992influence}. Capturing such processes require baroclinic models that represent the variations of water density along the water column. However, in regions where the water column is sufficiently homogeneous and shallow that vertical contrasts are negligible, ocean circulation is accurately approximated by barotropic models. Such models use a depth-averaged approach by assuming an homogeneous water column with constant density and are used to model estuaries, coastal regions and shelf seas \citep{tan1992shallow}. Both the baroclinic and the barotropic models usually rely on the hydrostatic equilibrium, \textit{i.e.} vertical accelerations are neglected by assuming that gravity balances the vertical component of the pressure gradient force. Such assumption is only valid when the horizontal scale of the flow is larger than its vertical scale \citep{cushman2011introduction}.}

In this thesis, we used the 2D barotropic version of the unstructured-mesh Second-generation Louvain-la-Neuve Ice-ocean Model (\href{https://www.slim-ocean.be/}{SLIM}). This model relies on Discontinuous Galerkin finite element methods \citep{aizinger2002discontinuous} and has already been successfully used to model the hydrodynamics \modif{of coastal regions and estuaries such as the whole Great Barrier Reef \citep{lambrechts2008multi}, the Florida Reef Tract \citep{frys2020fine}, the Scheldt estuary \citep{de2012water}, or the Mahakam delta \citep{sassi2011tidal}}. The 2D barotropic version of SLIM solves the shallow water equations, which assume a constant water density and compute depth-averaged current velocities. This model is therefore well suited for shallow areas where the water column is well mixed. Furthermore, assuming homogeneous vertical profiles reduces the computational cost and allows a finer spatial resolution of the model. However, in deeper areas or in regions where there is an inflow of freshwater, 3D baroclinic models are required to capture the effects of density discontinuities in the water column due to temperature and salinity gradients. Nonetheless, 3D baroclinic models are computationally more expensive, which currently prohibits the use of a reef-scale resolution on the whole Florida Reef Tract. As most Florida reefs are located in areas shallower than 30 meters (Fig. \ref{intro:bathy}), we coupled the 2D version of SLIM with GOM-HYCOM to indirectly capture the impact of baroclinic instabilities on the connectivity of the Florida Keys. Using this approach, \cite{frys2020fine} successfully modeled coral larval connectivity in the FRT with SLIM, \ie~the exchanges of larvae between reefs. \modif{The results of the model used in this thesis were validated against observations and showed good agreement with tide gauge and ADCP measurements \citep{dobbelaere2022connecting,dobbelaere2022impacts}}.

@@

\modif{As this thesis is mostly based on modeling tools, it relies on the main assumption that a mechanistic model can accurately capture transport processes in Florida's Coral Reef. Models are simplifications of the reality and hypotheses must therefore be made on the processes driving the evolution of the system under study. Such hypotheses were for instance made by favoring a fine resolution barotropic model over a coarser baroclinic model of the Florida Reef Tract. Furthermore, we assumed that if the modeled waves and hydrodynamics accurately reproduced local observations from buoys, tide gauges and ADCP, then the modeled transport that they drive would be reasonably accurate as well. According to the popular saying, "all models are wrong but some are useful". In the present study, model results are confronted against field observations and experimental results to identify the potential drivers of the dispersion of stressors in Florida's Coral Reef.}

@@

\newpage
\section*{Supporting publications}

>>>>

\modif{The motion of geophysical fluids such as seawater is characterized by the effects of ambient rotation and stratification \citep{cushman2011introduction}. The ambient rotation is induced by the Earth's spin and generates the Coriolis forces. Stratification arises from the presence of water masses with different temperatures and salinities, and therefore different densities. Under the action of the gravitational force, heavier water masses lower while lighter water masses rise, which causes the water column to tend towards a stable stratified equilibrium \citep{cushman2011introduction}. However, this equilibrium is disrupted in the presence of velocity gradients induced by wind and water motion \citep{miles1959generation}. These baroclinic instabilities generate internal waves, water mixing, and eddies \citep{cushman2011introduction}. Eddy activity is especially strong in boundary currents such as the Gulf Stream, where a strong horizontal shear occurs and where shelf water and deep water masses meet on the shelf break \citep{kourafalou2012florida}. These baroclinic instabilities were shown to have a significant impact on water composition and larval recruitment in the Florida Keys \citep{lee1992influence}. Capturing such processes require baroclinic models that represent the variations of water density along the water column. However, in regions where the water column is sufficiently homogeneous and shallow so that vertical gradients are negligible, the ocean circulation can be accurately approximated by a barotropic model. Such a model uses a depth-averaged approach by assuming an homogeneous water column with a constant density and is used to model coastal regions and shelf seas \citep{tan1992shallow}. Both the baroclinic and the barotropic models usually rely on the hydrostatic equilibrium, \textit{i.e.} vertical accelerations are neglected by assuming that gravity balances the vertical component of the pressure gradient force. Such assumption is only valid when the horizontal scale of the flow is larger than its vertical scale \citep{cushman2011introduction}.}

In this thesis, we used the 2D barotropic version of the unstructured-mesh Second-generation Louvain-la-Neuve Ice-ocean Model (\href{https://www.slim-ocean.be/}{SLIM}). This model relies on Discontinuous Galerkin finite element methods \citep{aizinger2002discontinuous} and has already been successfully used to model the hydrodynamics \modif{of coastal regions such as the whole Great Barrier Reef \citep{lambrechts2008multi}, the Florida Reef Tract \citep{frys2020fine}, the Scheldt estuary \citep{de2012water}, or the Mahakam delta \citep{sassi2011tidal}}. The 2D barotropic version of SLIM solves the shallow water equations, which assume a constant water density and compute depth-averaged current velocities. This model is therefore well suited for shallow areas where the water column is well mixed. Furthermore, assuming homogeneous vertical profiles reduces the computational cost and allows a finer spatial resolution of the model. However, in deeper areas or in regions where there is an inflow of freshwater, 3D baroclinic models are required to capture the effects of density discontinuities in the water column due to temperature and salinity gradients. Nonetheless, 3D baroclinic models are computationally more expensive, which currently prohibits the use of a reef-scale resolution on the whole Florida Reef Tract. As most Florida reefs are located in areas shallower than 30 meters (Fig. \ref{intro:bathy}), we coupled the 2D version of SLIM with GOM-HYCOM to indirectly capture the impact of baroclinic instabilities on the connectivity of the Florida Keys. Using this approach, \cite{frys2020fine} successfully modeled coral larval connectivity in the FRT with SLIM, \ie~the exchanges of larvae between reefs. \modif{The results of the model used in this thesis were validated against observations and showed good agreement with tide gauge and ADCP measurements \citep{dobbelaere2022connecting,dobbelaere2022impacts}}.

@@

\modif{As this thesis is mostly based on modeling tools, it relies on the main assumption that a mechanistic model can accurately capture transport processes in Florida's Coral Reef. Models are simplifications of the reality and hypotheses must therefore be made on the processes driving the evolution of the system under study. Such hypotheses were for instance made by favoring a fine resolution barotropic model over a coarser resolution baroclinic model of the Florida Reef Tract. Furthermore, we assumed that if the modeled waves and hydrodynamics accurately reproduced local observations from buoys, tide gauges and ADCP, then the modeled transport that they drive would be reasonably accurate as well. According to the popular saying, "all models are wrong but some are useful". In the present study, model results are confronted against field observations and experimental results to identify the potential drivers of the dispersion of stressors in Florida's Coral Reef.}

@@

\section*{Supporting publications}

### 2022-04-05 chapters/sctld/article.tex
modifs mise en page impression

\begin{table}
    \centering
    \begin{tabular}{|p{3cm}|p{4cm}|p{3.5cm}|}
        \hline
        \textbf{Indicators} & \textbf{Description} & \textbf{What it shows} \\
        \hline
            Weighted connectivity length (WCL) & 
            Average dispersal distance from origin to destination reef for all disease agents released over a reef & 
            Average distance that disease agents from a reef travels successfully to another reef \\
        \hline
            Out-degree &
            Number of out-going connections originating from a given reef multiplied by the total mass exchanged  &
            Overall potential for a reef to spread the disease \\
        \hline
            Fraction exchanged &
            Fraction of disease agents produced on a given reef that settles on other reefs &
            Relative likelihood of successful spread of the disease to other reefs  \\
        \hline
            Self-recruitment &
            Fraction of disease agents settling on a given reef that has been released on the same reef &
            Relative likelihood of unsuccessful spread of the disease from other reefs \\
        \hline            
    \end{tabular}
    \caption{Indicators used to analyze the modeled exchanges of infected material for each considered type of currents and for each simulated month.}
    \label{tab:indicator}
\end{table}

@@

	\includegraphics[width=.6\textwidth]{chapters/sctld/figures/network_sir.png}

@@

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{chapters/sctld/figures/connect_paper.jpg}
    \caption{Distribution of the indicators derived from the monthly connectivity matrices computed for each type of current during our simulated period. Mean values are indicated by white squares.}
    \label{fig:connect}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.95\textwidth]{chapters/sctld/figures/sir_obs.jpg}
    \caption{Disease prevalence averaged over all monitored sites over time as modeled by Eqs. \ref{eq:simplified} using calibrated transmission and removal parameters $\beta_0'=\frac{1}{6.45}~\text{days}^{-1}$ and $\sigma=\frac{1}{6.99}$ days$^{-1}$.}
    \label{fig:calibration}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{chapters/sctld/figures/sctld_validation_corrected.jpg}
    \caption{Summary of epidemiological model simulations with calibrated transmission parameters. \textbf{Top:} Modeled disease front speed for each type of current with respect to intra-reef 'infection' threshold $I_0$. \textbf{Bottom:} Mean distance between predicted diseased reefs and observed disease points. These results show that mean barotropic currents outperformed other modes of transport at reproducing the observed spread of the disease. The appearance of a plateau suggests that the modeled spread of the disease occurs for a well-defined range of values of $I_0$.}
    \label{fig:results}
\end{figure}

>>>>

\begin{table}
    \centering
    \begin{tabular}{|p{2.5cm}|p{3.5cm}|p{3.5cm}|}
        \hline
        \textbf{Indicators} & \textbf{Description} & \textbf{What it shows} \\
        \hline
            Weighted connectivity length (WCL) & 
            Average dispersal distance from origin to destination reef for all disease agents released over a reef & 
            Average distance that disease agents from a reef travels successfully to another reef \\
        \hline
            Out-degree &
            Number of out-going connections originating from a given reef multiplied by the total mass exchanged  &
            Overall potential for a reef to spread the disease \\
        \hline
            Fraction exchanged &
            Fraction of disease agents produced on a given reef that settles on other reefs &
            Relative likelihood of successful spread of the disease to other reefs  \\
        \hline
            Self-recruitment &
            Fraction of disease agents settling on a given reef that has been released on the same reef &
            Relative likelihood of unsuccessful spread of the disease from other reefs \\
        \hline            
    \end{tabular}
    \caption{Indicators used to analyze the modeled exchanges of infected material for each considered type of currents and for each simulated month.}
    \label{tab:indicator}
\end{table}

@@

	\includegraphics[width=.7\textwidth]{chapters/sctld/figures/network_sir.png}

@@

\begin{figure}
    \centering
    \includegraphics[width=.99\textwidth]{chapters/sctld/figures/connect_paper.jpg}
    \caption{Distribution of the indicators derived from the monthly connectivity matrices computed for each type of current during our simulated period. Mean values are indicated by white squares.}
    \label{fig:connect}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.99\textwidth]{chapters/sctld/figures/sir_obs.jpg}
    \caption{Disease prevalence averaged over all monitored sites over time as modeled by Eqs. \ref{eq:simplified} using calibrated transmission and removal parameters $\beta_0'=\frac{1}{6.45}~\text{days}^{-1}$ and $\sigma=\frac{1}{6.99}$ days$^{-1}$.}
    \label{fig:calibration}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.99\textwidth]{chapters/sctld/figures/sctld_validation_corrected.jpg}
    \caption{Summary of epidemiological model simulations with calibrated transmission parameters. \textbf{Top:} Modeled disease front speed for each type of current with respect to intra-reef 'infection' threshold $I_0$. \textbf{Bottom:} Mean distance between predicted diseased reefs and observed disease points. These results show that mean barotropic currents outperformed other modes of transport at reproducing the observed spread of the disease. The appearance of a plateau suggests that the modeled spread of the disease occurs for a well-defined range of values of $I_0$.}
    \label{fig:results}
\end{figure}

### 2022-04-05 include/thanks.tex
modifs mise en page impression

Mes premiers remerciements vont à mon promoteur, le professeur Emmanuel Hanert, le grand chef qui m'a guidé et accompagné tout au long de cette thèse. D'une énergie et surtout d'un optimisme à toute épreuve (si toutes ses prédictions s'étaient avérées exactes, cette thèse aurait été finie en 1 ans), il m’a poussé et soutenu durant les quatre dernières années. En outre, il a toujours réussi à accomplir le miracle de dégager du temps dans son agenda bien chargé pour me conseiller ou relire et commenter mon travail avec minutie.

@@

Ce travail a été financé par le Fonds de la Recherche Scientifique au moyen d’une bourse FRIA.

>>>>

Mes premiers remerciements vont à mon promoteur, le professeur Emmanuel Hanert, le grand chef qui m'a guidé et accompagné tout au long de cette thèse. D'une énergie et surtout d'un optimisme à toute épreuve (si toutes ses prédictions s'étaient avérées exactes, cette thèse aurait été finie en 1 ans), il m’a poussé et soutenu durant les quatre dernières années. En outre, il a toujours réussi à accomplir le miracle de dégager du temps dans son agenda bien chargé pour me conseiller ou relire et commenter mon travail avec minutie. Je tiens également à remercier tous les membres de mon jury pour le temps qu'ils ont accordé à la lecture de ce manuscrit ainsi que pour leurs judicieux conseils et suggestions lors de la défense privée.

@@

Ce travail a été financé par le Fonds de la Recherche Scientifique - FNRS au moyen d’une bourse FRIA.

### 2022-04-05 include/title.tex
new title
modifs mise en page impression

\thispagestyle{empty}
\begin{minipage}[b]{0.3\textwidth}
\hspace*{-0.8cm}\includegraphics[width=5.5cm]{./figures/logo_ucl.jpg}\vspace{0.35cm}
%\hspace*{3.4cm}\includegraphics[width=4.5cm]{./figures/orb.png}\vspace*{.1cm}
\end{minipage}
\begin{minipage}[b]{0.69\textwidth}
	\begin{center}
	\hspace*{0.5cm}Université catholique de Louvain\\
	\hspace*{0.5cm}\'Ecole Polytechnique de Louvain\\
	\hspace*{0.5cm} Earth and Life Institute\\
	\end{center}
\end{minipage}

\vspace*{3cm}
\hspace{-0.8cm}
\begin{minipage}{1.02\linewidth}
\centering
\LARGE\bfseries Florida's Coral Reef - Impact of ocean transport on management approaches % How modeling tools can inform coral reef management in the Florida Reef Tract
\end{minipage}

@@

\vspace*{0.5cm}
\footnotesize{
\hspace{-1cm}
\begin{tabular}{ll}
Prof. Emmanuel Hanert (Supervisor)   & UCLouvain \\
Prof. Eric Deleersnijder             & UCLouvain\\
Dr. Jonathan Lambrechts              & UCLouvain \\
Prof. Claire B. Paris-Limouzy        & University of Miami, USA \\
Dr. Christopher Thomas               & Risk Management Solutions, UK \\
Prof. Marnik Vanclooster (President) & UCLouvain
\end{tabular}
}

\textcolor{white}{Et pour la tradition, Régis Malpas \& Marc-Henry Comans}

@@

\vspace*{.5cm}
\vspace*{\stretch{1}}
\begin{minipage}{\textwidth}
\centering
\large Louvain-la-Neuve, February 16, 2022
\end{minipage}

>>>>

\thispagestyle{empty}
\begin{minipage}[b]{0.3\textwidth}
\hspace*{-0.8cm}\includegraphics[width=5.5cm]{./figures/logo_ucl.jpg}\vspace{0.1cm}
%\hspace*{3.4cm}\includegraphics[width=4.5cm]{./figures/orb.png}\vspace*{.1cm}
\end{minipage}
\begin{minipage}[b]{0.69\textwidth}
	\begin{center}
	\hspace*{0.5cm}Université catholique de Louvain\\
	\hspace*{0.5cm}\'Ecole Polytechnique de Louvain\\
	\hspace*{0.5cm} Earth and Life Institute\\
	\end{center}
\end{minipage}

\vspace*{2cm}
\hspace{-0.8cm}
\begin{minipage}{1.02\linewidth}
\centering
\LARGE\bfseries Modeling local and regional dispersion of stressors in Florida's Coral Reef
\end{minipage}

@@

\vspace*{0.5cm}
\footnotesize{
\hspace{-1cm}
\begin{tabular}{ll}
Prof. Emmanuel Hanert (Supervisor)   & UCLouvain \\
Prof. Eric Deleersnijder             & UCLouvain\\
Dr. Jonathan Lambrechts              & UCLouvain \\
Prof. Claire B. Paris-Limouzy        & University of Miami, USA \\
Dr. Christopher Thomas               & Risk Management Solutions, UK \\
Prof. Marnik Vanclooster (President) & UCLouvain
\end{tabular}
}
\newline
\vspace*{4em}
\newline
\textcolor{white}{Et pour la tradition, Régis Malpas \& Marc-Henry Comans}

@@

\vspace*{.5cm}
\vspace*{\stretch{1}}
\begin{minipage}{\textwidth}
\centering
\large Louvain-la-Neuve, April 25, 2022
\end{minipage}

### 2022-04-05 thesis.tex
modifs mise en page impression

\documentclass[twoside,12pt,a4paper,openright]{memoir}
\maxsecnumdepth{subsubsection}			%Automatically number sections down to ``section'' level
\setsecnumdepth{subsubsection}
% \hyphenation{de-leer-snij-der}
\usepackage[utf8]{inputenc}			%Optimal font encoding for most latin languages
\usepackage[T1]{fontenc}
\usepackage{changepage}
\usepackage{pgfplots}
\usepackage{bm}
\usepackage{lipsum}
\input{include/specific_headers.tex}
\newcommand{\GG}[1]{}
\pgfplotsset{compat=1.15}
\usepackage[pdftex,linktocpage]{hyperref}		%For hyperlinks within doc, and setting doc info
\hypersetup{pdftitle={Florida's Coral Reef - Impact of ocean transport on management approaches}}
\hypersetup{pdfauthor={Thomas DOBBELAERE}}
\hypersetup{pdfsubject={Florida's Coral Reef - Impact of ocean transport on management approaches}}
\hypersetup{pdfkeywords={Biophysical modeling, Florida Coral Reef, SCTLD, SLIM}}
% % Comment out next hypersetup section for print version:
%\hypersetup{
%  colorlinks=true,
%  citecolor=blue,
%  linkcolor=blue,
%  urlcolor=blue
%}
\hypersetup{
  colorlinks=true,
  citecolor=black,
  linkcolor=black,
  urlcolor=black
}
% % % %   citebordercolor={0.8 0.8 0.8},
% % % %   filebordercolor={0.8 0.8 0.8},
% % % %   linkbordercolor={0.8 0.8 0.8},
% % % %   menubordercolor={0.8 0.8 0.8},
% % % %   urlbordercolor={0.8 0.8 0.8},
% % % %   runbordercolor={0.8 0.8 0.8}

@@

\begin{document}
\frontmatter
  \input{include/title}
  \clearemptydoublepage
  \input{include/abstract}
  \clearemptydoublepage
  %\input{include/thanks}
  %\clearemptydoublepage
  \tableofcontents
  \clearemptydoublepage
  \input{include/glossary}
  \clearemptydoublepage
  \mainmatter 
%%%%
\mychapter{Introduction} \label{chap:intro}
 \input{chapters/intro/intro}
%%%%%% 
\mychapter{Processes driving the spread of stony coral tissue loss disease through the Florida Reef Tract} \label{chap:sctld}
\chaptermark{Processes driving the spread of SCTLD in the FRT}  
\input{chapters/sctld/sctld}
\mychapter{Transmission dynamics of the disease from the Marquesas and to the Dry Tortugas}\label{chap:drto}
\chaptermark{Transmission of SCTLD from the Marquesas to the DRTO}  
\input{chapters/drto/drto}
\mychapter{The onset of the outbreak and the PortMiami Deep Dredge Project} \label{chap:onset}
\chaptermark{Onset of SCTLD and PortMiami Deep Dredge Project}  
\input{chapters/onset/onset}
\mychapter{Impacts of hurricanes on transport processes in the Florida Keys} \label{chap:irma}
\chaptermark{Wave-induced transport under hurricanes}
\input{chapters/irma/irma}
%%%%%%%%%%%
%
%%%%%  
%%%
  \mychapter{Conclusions and perspectives} \label{chap:conclusion}
  \input{chapters/conclusions/conclusions}    
%%
%
  \clearemptydoublepage
  \bibliography{include/bibliography.bib}

>>>>

\documentclass[twoside,12pt,a4paper,openright]{memoir}
\maxsecnumdepth{subsubsection}			%Automatically number sections down to ``section'' level
\setsecnumdepth{subsubsection}
% \hyphenation{de-leer-snij-der}
\usepackage[utf8]{inputenc}			%Optimal font encoding for most latin languages
\usepackage[T1]{fontenc}
\usepackage{changepage}
\usepackage{pgfplots}
\usepackage{bm}
\usepackage{lipsum}
\input{include/specific_headers.tex}
\newcommand{\GG}[1]{}
\pgfplotsset{compat=1.15}
\usepackage[pdftex,linktocpage]{hyperref}		%For hyperlinks within doc, and setting doc info
\hypersetup{pdftitle={Florida's Coral Reef - Impact of ocean transport on management approaches}}
\hypersetup{pdfauthor={Thomas DOBBELAERE}}
\hypersetup{pdfsubject={Modeling local and regional dispersion of stressors in Florida's Coral Reef}}
\hypersetup{pdfkeywords={Biophysical modeling, Florida Coral Reef, SCTLD, SLIM}}
% % Comment out next hypersetup section for print version:
%\hypersetup{
%  colorlinks=true,
%  citecolor=blue,
%  linkcolor=blue,
%  urlcolor=blue
%}
\hypersetup{
  colorlinks=true,
  citecolor=black,
  linkcolor=black,
  urlcolor=black
}
% % % %   citebordercolor={0.8 0.8 0.8},
% % % %   filebordercolor={0.8 0.8 0.8},
% % % %   linkbordercolor={0.8 0.8 0.8},
% % % %   menubordercolor={0.8 0.8 0.8},
% % % %   urlbordercolor={0.8 0.8 0.8},
% % % %   runbordercolor={0.8 0.8 0.8}

@@

\begin{document}
\frontmatter
  \input{include/title}
  \clearemptydoublepage
  \input{include/abstract}
  \clearemptydoublepage:
  \input{include/thanks}
  \clearemptydoublepage
  \tableofcontents
  \clearemptydoublepage
  \input{include/glossary}
  \clearemptydoublepage
  \mainmatter 
%%%%
\mychapter{Introduction} \label{chap:intro}
 \input{chapters/intro/intro}
%%%%%% 
\mychapter{Processes driving the spread of stony coral tissue loss disease through the Florida Reef Tract} \label{chap:sctld}
\chaptermark{Processes driving the spread of SCTLD in the FRT}  
\input{chapters/sctld/sctld}
\mychapter{Transmission dynamics of the disease from the Marquesas and to the Dry Tortugas}\label{chap:drto}
\chaptermark{Transmission of SCTLD to the DRTO}  
\input{chapters/drto/drto}
\mychapter{The onset of the outbreak and the PortMiami Deep Dredge Project} \label{chap:onset}
\chaptermark{The onset of SCTLD and the PMDDP}  
\input{chapters/onset/onset}
\mychapter{Impacts of hurricanes on transport processes in the Florida Keys} \label{chap:irma}
\chaptermark{Wave-induced transport under hurricanes}
\input{chapters/irma/irma}
%%%%%%%%%%%
%
%%%%%  
%%%
  \mychapter{Conclusions and perspectives} \label{chap:conclusion}
  \input{chapters/conclusions/conclusions}    
%%
%
  \clearemptydoublepage
  \bibliography{include/bibliography.bib}
